Deterministic Scheduling of Periodic Messages for Cloud RAN

### 2017-07-24 infocom/infocom.tex
regression

%\documentclass[a4paper,10pt]{article}
\documentclass[10pt, conference, letterpaper]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{url}
\usepackage{graphicx,graphics} 
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{complexity}
\usepackage{tkz-graph}
\usepackage{float}
\usepackage{tabularx}
\usepackage{setspace}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{authblk}
% \usepackage{hyperref}

@@

 In this article, we study mechanisms to deal with the latency and periodicity constraints in the network located between the BUUs and the RRHs called \emph{fronthaul}.
 Statistical multiplexing even with a large bandwidth does not comply with the latency requirements. Therefore, the current solution~\cite{pizzinat2015things,tayq2017real} is to use dedicated circuits for the fronthaul. Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches. This architecture is very expensive and hardly scales in the case of a mobile network composed of about $10000$ base stations. Here we propose to use a deterministic approach to schedule our periodic messages. This approach has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}. Several patents on concepts and mechanisms for DetNet have been already published, see for example~\cite{howe2005time,leclerc2016transmission}. The aim is to operate a C-RAN on a low-cost shared switched network.

@@

      \begin{center}
	 \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{periode_petite.pdf}
      \end{center}
            \vspace{-0.75cm}
      \caption{Minimum period averaged over $1000$ random instances}\label{fig:short}
      \end{figure}
      First, we remark that the period found by the exhaustive search is only very slightly above the lower bound of $n\tau$, which means that, in this regime, it is very well justified to look for a solution without waiting time even for a highly loaded network.

@@

       \begin{center}
      \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{echec_longues.pdf}
      \end{center}
            \vspace{-1cm}
      \caption{Success rate for $8$ routes over $1000$ random instances}\label{fig:long}
     \end{figure}

@@

     The random order is the best by far. When the load is not too high ($P = 30,000$) there is always a solution with margin $0$.
     Note that, when disallowing waiting times, there were instances without solutions for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the \pall problem. We now want to compare the performances of the three different algorithms used in the second stage. Since GD already showed excellent results on mild loads, it is more interesting to focus on the behavior of the algorithms on high load. Moreover, we will use $1,000$ random orders for the first stage as it gives the best results. The following experiment is realized on routed networks with $8$ routes, weights of the arcs drawn between $0$ and $20,000$ and with a period of $21,000$.  We represent the success rate with regards to the margin, for the three algorithms computed over $10,000$ random star routed networks. 
    \begin{figure} [h] 
      \vspace{-0.5cm}
       \begin{center}
      \includegraphics[width=0.5\textwidth]{retour_21000.pdf}
      \end{center}
            \vspace{-1cm}
      \caption{Success rate of GD, MLS and PMLS for $P = 21000$}
     \label{fig:success21000}
       \vspace{-0.2cm}
     \end{figure}
     The MLS algorithm performs poorly, worst than GD and PMLS, which shows that taking into account the periodicity is fundamental.
     The GD algorithms is close to $100\%$ success rate for margins larger than $1,500$ while the PMLS algorithm finds a solution in more than $95\%$ of the experiments, even with a margin $0$. Therefore, for the worst possible constraints on load and margin, there are a few instances for which we do not find a solution. However, with a margin of $1,000$, which corresponds to about $0.05$ms of additional delay with the chosen parameters, we always find a solution.

    Remark that the random order corresponds to the best of $1,000$ orders drawn uniformly which means that a computation can be up to $1,000$ time slower than for a fixed order. The choice of the number of random orders drawn yields a trade-off between the computation time and the success rate. Up to now, we chose $1,000$ random orders arbitrarily. We investigate the success rate of our algorithm with regards to the number of random orders drawn, a period of $21,000$ and a margin $0$. The following tables presents the average success rate for each number of sending orders, on $1,000$ instances, for GD and PMLS.
         \begin{figure}[h] 
       \begin{center}
   \begin{tabularx}{0.5\textwidth}{|c|X|X|X|X|X|X|}
    \hline
    \# orders& $1$ & $10$ & $100$& $1,000$& $10^{4}$&$10^{5}$\\
    \hline
    GD & $0.6$ &$7.1$&$33.4$&$76.4$&$90.0$&$90.0$\\
    \hline
  PMLS & $41.1$ &$82.5$&$94.5$&$96.2$&$97.2$&$97.2$\\
    \hline
      \end{tabularx}
      \end{center}
   \caption{Impact of the number of random sending orders}
     \end{figure}
First remark that we can improve our previous results by taking $10000$ random orders, which 
yields the best results for the two algorithms. The number of different orders is $7!= 5,040$ since we have $8$ routes and the solutions are invariant up to a circular permutation of the order. Therefore instead of doing $10000$ random draws we could test every possible order in less time. However this method would not be practical with regard to the computation time for $n = 15$. On the other hand, remark that the success rate of PMLS is already high for $100$ random orders, which means it will work even better than the other methods when $n$ is larger and that the number of random orders drawn is critical.

     Now that we have found the best amongst the algorithms solving \pall, we need to compare its performances against the actual way to manage the messages in a network. The classical way to manage messages in the network is statistical multiplexing, where there is a FIFO buffer in each node of the network to deal with the collisions. The time at which the messages are sent in the network is not computed as in our approach, thus we fix the offsets of each route to some random value.
     Even if this policy seems to work in practice when the network is not too loaded, it does not give any guarantee on the latency. Remark that the process is not periodic, therefore we must measure the process time of each route over several periods if we want to compute its maximum. We choose to simulate it for $1000$ periods and we have observed that the process time usually stabilizes after $10$ periods. The margin is defined as the maximum process time, computed as explained, minus twice the size of the longest route.

     We draw $1000$ star routed networks with $8$ routes, with weights on the arcs drawn between $0$ and $20,000$. Note that the results are almost the same when the arcs are small. We measure, for periods from $20000$ (network fully loaded), to $50,000$ ($40 \%$ of load), the median, the first, and the third quartile of the margins computed in $1000$ simulations using FIFO buffer to resolve collisions.

>>>>

%\documentclass[a4paper,10pt]{article}
\documentclass[10pt, conference, letterpaper]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{url}
\usepackage{graphicx,graphics} 
\usepackage{color}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{complexity}
\usepackage{tkz-graph}
\usepackage{float}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage{icomma}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{authblk}
% \usepackage{hyperref}

@@

 In this article, we study mechanisms to deal with the latency and periodicity constraints in the network located between the BUUs and the RRHs called \emph{fronthaul}.
 Statistical multiplexing even with a large bandwidth does not comply with the latency requirements. Therefore, the current solution~\cite{pizzinat2015things,tayq2017real} is to use dedicated circuits for the fronthaul. Each end-point (RRH on one side, BBU on the other side) is connected through direct fiber or full optical switches. This architecture is very expensive and hardly scales in the case of a mobile network composed of about $1
 0$ base stations. Here we propose to use a deterministic approach to schedule our periodic messages. This approach has gained some traction recently: Deterministic Networking is under standardization in IEEE 802.1 TSN group~\cite{finn-detnet-architecture-08}, as well at IETF DetNet working group~\cite{ieee802}. Several patents on concepts and mechanisms for DetNet have been already published, see for example~\cite{howe2005time,leclerc2016transmission}. The aim is to operate a C-RAN on a low-cost shared switched network.

@@

      \begin{center}
	 \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{periode_petite.pdf}
      \end{center}
            \vspace{-0.75cm}
      \caption{Minimum period averaged over $1,000$ random instances}\label{fig:short}
      \end{figure}
      First, we remark that the period found by the exhaustive search is only very slightly above the lower bound of $n\tau$, which means that, in this regime, it is very well justified to look for a solution without waiting time even for a highly loaded network.

@@

       \begin{center}
      \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{echec_longues.pdf}
      \end{center}
            \vspace{-1cm}
      \caption{Success rate for $8$ routes over $1,000$ random instances}\label{fig:long}
     \end{figure}

@@

     The random order is the best by far. When the load is not too high ($P = 30,000$) there is always a solution with margin $0$.
     Note that, when disallowing waiting times, there were instances without solutions for these parameters (see Section~\ref{sec:exp_PAZL}), which justifies the interest of studying the \pall problem. We now want to compare the performances of the three different algorithms used in the second stage. Since GD already showed excellent results on mild loads, it is more interesting to focus on the behavior of the algorithms on high load. Moreover, we will use $1,000$ random orders for the first stage as it gives the best results. The following experiment is realized on routed networks with $8$ routes, weights of the arcs drawn between $0$ and $20,000$ and with a period of $21,000$.  We represent the success rate with regards to the margin, for the three algorithms computed over $10,000$ random star routed networks. 
    \begin{figure} [h] 
      \vspace{-0.5cm}
       \begin{center}
      \includegraphics[width=0.5\textwidth]{retour_21000.pdf}
      \end{center}
            \vspace{-1cm}
      \caption{Success rate of GD, MLS and PMLS for $P = 21,000$}
     \label{fig:success21000}
       \vspace{-0.2cm}
     \end{figure}
     The MLS algorithm performs poorly, worst than GD and PMLS, which shows that taking into account the periodicity is fundamental.
     The GD algorithms is close to $100\%$ success rate for margins larger than $1,500$ while the PMLS algorithm finds a solution in more than $95\%$ of the experiments, even with a margin $0$. Therefore, for the worst possible constraints on load and margin, there are a few instances for which we do not find a solution. However, with a margin of $1,000$, which corresponds to about $0.05$ms of additional delay with the chosen parameters, we always find a solution.

    Remark that the random order corresponds to the best of $1,000$ orders drawn uniformly which means that a computation can be up to $1,000$ time slower than for a fixed order. The choice of the number of random orders drawn yields a trade-off between the computation time and the success rate. Up to now, we chose $1,000$ random orders arbitrarily. We investigate the success rate of our algorithm with regards to the number of random orders drawn, a period of $21,000$ and a margin $0$. The following tables presents the average success rate for each number of sending orders, on $1,000$ instances, for GD and PMLS.
         \begin{figure}[h] 
       \begin{center}
   \begin{tabularx}{0.5\textwidth}{|c|X|X|X|X|X|X|}
    \hline
    \# orders& $1$ & $10$ & $100$& $1,000$& $10^{4}$&$10^{5}$\\
    \hline
    GD & $0.6$ &$7.1$&$33.4$&$76.4$&$90.0$&$90.0$\\
    \hline
  PMLS & $41.1$ &$82.5$&$94.5$&$96.2$&$97.2$&$97.2$\\
    \hline
      \end{tabularx}
      \end{center}
   \caption{Impact of the number of random sending orders}
     \end{figure}
First remark that we can improve our previous results by taking $10,000$ random orders, which 
yields the best results for the two algorithms. The number of different orders is $7!= 5,040$ since we have $8$ routes and the solutions are invariant up to a circular permutation of the order. Therefore instead of doing $10,000$ random draws we could test every possible order in less time. However this method would not be practical with regard to the computation time for $n = 15$. On the other hand, remark that the success rate of PMLS is already high for $100$ random orders, which means it will work even better than the other methods when $n$ is larger and that the number of random orders drawn is critical.

     Now that we have found the best amongst the algorithms solving \pall, we need to compare its performances against the actual way to manage the messages in a network. The classical way to manage messages in the network is statistical multiplexing, where there is a FIFO buffer in each node of the network to deal with the collisions. The time at which the messages are sent in the network is not computed as in our approach, thus we fix the offsets of each route to some random value.
     Even if this policy seems to work in practice when the network is not too loaded, it does not give any guarantee on the latency. Remark that the process is not periodic, therefore we must measure the process time of each route over several periods if we want to compute its maximum. We choose to simulate it for $1,000$ periods and we have observed that the process time usually stabilizes after $10$ periods. The margin is defined as the maximum process time, computed as explained, minus twice the size of the longest route.

     We draw $1,000$ star routed networks with $8$ routes, with weights on the arcs drawn between $0$ and $20,000$. Note that the results are almost the same when the arcs are small. We measure, for periods from $20,000$ (network fully loaded), to $50,000$ ($40 \%$ of load), the median, the first, and the third quartile of the margins computed in $1,000$ simulations using FIFO buffer to resolve collisions.
